%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Software Engineer} % Job title
{Asurint} % Organization
{Cleveland, Ohio} % Location
{Jan 2019 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed systems for automatically gathering data from many court websites.}
\item {Led and delegated tasks to a team of near-shore workers.}
\item {Wrote code with an emphasis on high quality, maintainability, and performance.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Senior Software Engineer} % Job title
{Vertical Knowledge} % Organization
{Chagrin Falls, Ohio} % Location
{Nov 2016 - Dec 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Architected and implemented portions of a system collecting large volumes of publicly available information.}
\item {Mentored junior developers.}
\item {Developed tutorials and documentation for client-facing APIs.}
\item {Maintained legacy system before transitioning users to its replacement.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Developer and Technology Consultant} % Job title
{Self-employed} % Organization
{Mentor, Ohio} % Location
{May 2001 - Nov 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed full-stack web applications as a consultant for Offerpop, Color Splash Studio, University of Michigan, and others.}
\item {Built custom video and networking solutions on embedded systems, including Raspberry Pi and Arduino devices.}
\item {Consistently completed projects within estimated timeframes.}
\item {Designed and programmed interactive Konfabulator Widgets for various clients and general public using JavaScript.}
\item {Recorded and edited professional videos for school and community events.}
\item {Created WordPress plugins and themes.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Development Instructor} % Job title
{We Can Code IT} % Organization
{Cleveland, Ohio} % Location
{May 2016 - Oct 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
% \item {Designed and taught full-time boot camp courses in web development using C\#, MVC, and Entity Framework.}
\item {Addressed needs of a diverse student population and adapted teaching to meet various learning styles.}
\item {Rebuilt curriculum to meet accelerated goals based upon employer feedback.}
\item {Acted as product owner and mentor to guide students through building complex final projects following Scrum methodology.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Data Science Instructor and Online Content Author} % Job title
{The Iron Yard} % Organization
{Durham, North Carolina} % Location
{Jun 2015 - Apr 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Taught intensive 12-week full-time ``boot camp" courses in web development and data science using Python, Django, and Pandas.}
\item {Planned and led crash course workshops introducing new developers to the joy of programming.}
\item {Mentored and managed students through the planning and execution of marketable final projects.}
\item {Created online lessons covering a wide variety of topics relating to web development.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Director of Center for Technology \& Invention, Upper School Technology Department Chair, Teacher} % Job title
{Hathaway Brown School} % Organization
{Shaker Heights, Ohio} % Location
{Aug 2008 - Jun 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Oversaw and mentored programs encouraging and recognizing students to pursue engineering, including a high school robotics team.}
\item {Laid the groundwork for the creation of a schoolwide digital fabrication lab, securing funding and administrative support.}
\item {Used low-power systems such as Raspberry Pi and Arduino in applications ranging from computer vision to hacking remote control cars.}
\item {Selected and guided students in the pursuit of intense creative projects, including designing a golf course and creating a video game.}
\item {Created and taught computer science classes for 5th-12th grade girls ranging from introductory to Post-Advanced Placement.}
\item {Served as a key member of the Technology Review Committee, spearheading campus-wide wifi and a 1:1 program for students.}
\item {Provided technical support for faculty and staff while promoting more technology independence via workshops and user groups.}
\item {Presented at educational technology conferences on using the Python programming language as part of an introductory course.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Computer Programmer I} % Job title
{Manatron} % Organization
{Portage, Michigan} % Location
{Jun 2005 - Jan 2006} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed, profiled, and optimized .NET web applications.}
\item {Enhanced developer tools for automated project building.}
\item {Transitioned a large codebase from .NET 1.1 to .NET 2.0.}
\item {Identified and fixed errors in existing code.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}